---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
options(tibble.width = Inf)
```

blorr: Tools for building binary logistic regression models 
------------

**Author:** [Aravind Hebbali]()<br/>
**License:** [MIT](https://opensource.org/licenses/MIT)

[![CRAN status](http://www.r-pkg.org/badges/version/blorr)](https://cran.r-project.org/package=blorr) [![Travis build status](https://travis-ci.org/rsquaredacademy/blorr.svg?branch=master)](https://travis-ci.org/rsquaredacademy/blorr) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/rsquaredacademy/blorr?branch=master&svg=true)](https://ci.appveyor.com/project/rsquaredacademy/blorr) [![Coverage status](https://codecov.io/gh/rsquaredacademy/blorr/branch/master/graph/badge.svg)](https://codecov.io/github/rsquaredacademy/blorr?branch=master) ![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)

Tools designed to make it easier for users, particularly beginner/intermediate R users to build logistic regression models. Includes comprehensive regression 
output, variable selection procedure and model validation statistics.

### Installation

You can install blorr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("rsquaredacademy/blorr")
```

### Shiny App

Use `blr_launch_app()` to explore the package using a shiny app.

## Vignettes

- [Bivariate Analysis](https://blorr.rsquaredacademy.com/bivariate_analysis.html)
- [Model Fit Statistics](https://blorr.rsquaredacademy.com/intro.html)
- [Model Validation](https://blorr.rsquaredacademy.com/model_validation.html)
- [Variable Seelction](https://blorr.rsquaredacademy.com/variable_selection.html)
- [Residual Diagnostics](https://blorr.rsquaredacademy.com/residual_diagnostics.html)


### Consistent Prefix

blorr uses consistent prefix `blr_*` for easy tab completion.

### Quick Overview

```{r libs}
library(blorr)
library(magrittr)
```

#### Bivariate Analysis 

```{r bivar}
blr_bivariate_analysis(hsb2, honcomp, female, prog, race, schtyp)
```

#### Weight of Evidence & Information Value

```{r woeiv}
blr_woe_iv(hsb2, prog, honcomp)
```

#### Model

```{r model}
# create model using glm
model <- glm(honcomp ~ female + read + science, data = hsb2,
             family = binomial(link = 'logit'))
```

#### Regression Output

```{r regress}
blr_regress(model)
```

#### Model Fit Statistics

```{r mfs}
blr_model_fit_stats(model)
```

#### Confusion Matrix

```{r conf}
blr_confusion_matrix(model)
```

#### Hosmer Lemeshow Test

```{r hoslem}
blr_test_hosmer_lemeshow(model)
```

#### Gains Table

```{r gains}
blr_gains_table(model)
```

#### Lift Chart

```{r lift}
model %>%
  blr_gains_table() %>%
  plot()
```

#### ROC Curve

```{r roc}
model %>%
  blr_gains_table() %>%
  blr_roc_curve()
```

#### KS Chart

```{r kschart}
model %>%
  blr_gains_table() %>%
  blr_ks_chart()
```

#### Lorenz Curve

```{r}
blr_lorenz_curve(model)
```

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
