---
title: "Bivariate Analysis"
author: "Aravind Hebbali"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Bivariate Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Introduction

The blorr package offers tools for building and validating binary logistic regression models. It 
is most suitable for beginner/intermediate R users and those who teach statistics using R. The API
is very simple and most of the functions take either a data.frame/tibble or a model as input. **blorr** use
consistent prefix **blr_** for easy tab completion. The below diagram shows the API design:

This document is a quick start guide to the tools offered by **blorr**. Other vignettes provide more details on 
specific topics:

- Bivariate Analysis
- Variable Selection
- Residual Diagnsotics
- Model Validation

### Libraries

```{r libs}
library(blorr)
library(magrittr)
```

### Data

We will use the bank marketing data set. 


### Bivariate Analysis

```{r bivar1}
blr_bivariate_analysis(bank_marketing, y, job, marital, education, default, housing, 
  loan, contact, poutcome)
```

### Weight of Evidence & Information Value


```{r woe1}
blr_woe_iv(bank_marketing, job, y)
```

#### Plot

```{r woeplot}
k <- blr_woe_iv(bank_marketing, job, y)
plot(k)
```

#### Multiple Variables

```{r woe2}
blr_woe_iv_stats(bank_marketing, y, job, marital, education, default, housing, 
  loan, contact, poutcome)
```


